plantecophys - an R package for analysing and modelling leaf gas exchange data

### 2015-09-10 manuscript.Rmd
Made code work with data downloaded from figshare; edits to example application

\
Because the fitting uses non-linear least squares, standard methods can be employed to estimate standard errors (SE), confidence intervals, and correlation of the fitted parameters. The fitaci function returns by default the SE and confidence intervals, and the built-in help page for the fitaci function shows how the nlstools package can be used to provide a detailed overview of the statistics of the non-linear least squares fit.

@@

To demonstrate a practical application of the key functions in the package, I use field-collected data from Medlyn et al. [-@medlyn2007] on *Eucalyptus delegatensis*. Both A-C~i~ curves and 'spot gas exchange' data (i.e. leaf gas exchange measurements at prevailing environmental conditions) were collected. Using the `fitacis` function, it is straightforward to fit all `r length(acifits)` curves to the A-C~i~ data, and make standard plots of the fitted curves (shown in Fig. 5a). The fitted coefficients are easily extracted, and used to plot a standard comparison of fitted V~cmax~ and J~max~ values (Fig. 5b), which show the typical correlation between the two. Next I fit the spot gas exchange data, yielding estimates of g~1~ and (optionally) g~0~, and we can quickly compare modelled to measured g~s~ (Fig. 5c), and compare the model prediction of instantaneous transpiration efficiency (A~n~/E) to measurements along the variation in D (Fig. 5d). This simple example application is available in the published repository (see Methods). The simplified code for this example (panels a-c), omitting special formatting and a few minor settings is given below.

@@

# Acknowledgments {.unnumbered}
David Ellsworth, Belinda Medlyn and Martin De Kauwe are acknowledged for discussions on fitting A-C~i~ curves. Special thanks to Belinda Medlyn for the code in the MAESTRA model which provided the basis for an early version of the Photosyn function, and for sharing the data used in the example application. Thanks to John Drake and Nick Smith for testing and suggesting new features.

>>>>

\
Because the fitting uses non-linear least squares, standard methods can be employed to estimate standard errors (SE), confidence intervals, and correlation of the fitted parameters. The `fitaci` function returns by default the SE and confidence intervals, and the built-in help page for the `fitaci` function shows how the `nlstools` package can be used to provide a detailed overview of the statistics of the non-linear least squares fit.

@@

To demonstrate a practical application of the key functions in the package, I use field-collected data from Medlyn et al. [-@medlyn2007] on *Eucalyptus delegatensis*. Both A-C~i~ curves and 'spot gas exchange' data (i.e. leaf gas exchange measurements at prevailing environmental conditions) were collected. Using the `fitacis` function, it is straightforward to fit all `r length(acifits)` curves to the A-C~i~ data, and make standard plots of the fitted curves (shown in Fig. 5a). The fitted coefficients are easily extracted, and used to plot a standard comparison of fitted V~cmax~ and J~max~ values (Fig. 5b), which show the typical correlation between the two.

\
Next, I fit Eq. 4 to the spot gas exchange data, yielding an estimate of g~1~ (Fig. 5c). It is straightforward to compare modelled to measured g~s~ (Fig. 5c), and compare the model prediction of instantaneous transpiration efficiency (A~n~/E) to measurements along the variation in D (Fig. 5d). Because `fitBB` can fit a number of Ball-Berry type variants, the various models can be easily compared in terms of goodness of fit. This simple example application is available in the published repository (see Methods), and simplified code for this example (panels a-c only), omitting special formatting and a few minor settings, is given below.

@@

# Acknowledgments {.unnumbered}
David Ellsworth, Belinda Medlyn and Martin De Kauwe are acknowledged for discussions on fitting A-C~i~ curves. Special thanks to Belinda Medlyn for the code in the MAESTRA model which provided the basis for an early version of the `Photosyn` function, and for sharing the data used in the example application. Thanks to John Drake for testing and suggesting new features.
